---
title: "Week3: Image Analysis Using Fiji"
author: "Kaitlyn Li"
date: "9/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(knitr)
library(readr)
library(moderndive)
library(infer)
```



```{r, include = FALSE}
options(httr_oob_default = TRUE)
library(tidyverse)
library(googlesheets4)
url <- "https://docs.google.com/spreadsheets/d/1kxY0uaV1wS1OGlqn60fGKX9fVdjwCezsi7WakJBdyUw/edit?usp=sharing"
pt_1 <- read_sheet(ss = url,
                     sheet = "Part 1")
pt_2 <- read_sheet(ss = url,
                     sheet = "Part 2")
tidy_pt_2 <- read_sheet(ss = url,
                     sheet = "Pt2tidy")
```



```{r, echo=FALSE, fig.cap = "Figure 1. A scatter plot depicting the observation of contracted cells in two conditions (A and B) grouped by observer. In this plot, the error bars are calculated by the function `stat_summary` and shown by condition, considering the three observers and 3 images as replicates of the same experiment."}
ggplot(data = pt_1, aes(x = Condition, y = Proportion, color = Observer))+ 
  geom_jitter(width = 0.45) +
  labs(x = "Condition", y = "Fraction Contracted", title = "Observation of Contracted Cells in 2 Conditions") +
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red")


```




```{r, echo=FALSE}
ggplot(data = tidy_pt_2, aes(x = Condition, y = A_M_Ratio, color = Condition))+ 
  geom_jitter(width = 0.45) +
  labs(x = "Condition", y = "Ratio of Mean Fluorescence", title = "Ratio of Myosin and Actin Mean Gray Values") +
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
        geom="errorbar", color="red", width=0.2) +
  stat_summary(fun.y=mean, geom="point", color="red")
```





## Questions to Answer  
1. In part 1 and 2 what was your n? Why did you choose that value to be your n over other
possibilities? Did you use different n in Part 1 and Part 2. How does this affect your error
bars (i.e. the s.e.m).  



2. What is the “bit-depth” of your image. You can find out by going to the “Image” header
and scrolling to “Type” tab. Your image should be 16-bit, what does that mean?  

Bit-depth is the amount of information an image carries. A standard JPEG image is 8-bit, while ours is 16-bit. This means that our image contains a lot of information in colors and tones that can help us better analyze the cells than just looking at a phone camera picture of them. Even if we can't see all the details, Fiji helps us calculate things by getting into the nitty gritty details.

3. If you multiply the “Area” by the “Mean Gray Value” of your box what value does that
give you?  

  The value given by multiplying "Area" and "Mean Gray Value" is the integrated density. Integration is usually used to find the area under a curve, so it makes sense if the Gray Value is like a curve. 